DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-07 paper/comparison.tex
Edited comparison

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
, and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much as most of the neural network computation
is done at the GPU.

@@

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observe dramatic execution time
increase, up to 9.4X, in Raspberry Pi 3 as we increase the number of
co-scheduled tasks. We also observe increased control loop execution
timing in Intel Up and TX2, but the degree of the increase is not as
dramatic as the Pi3. Compared to their respective solo timing (i.e.,
the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increase, respectively. This is somewhat suprising
because Raspberry Pi 3's cores are in-oder architecture based while
the cores in Intel Up and NVIDIA TX2 are out-of-order architecture
based and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

>>>>

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
, and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much as most of the neural network computation
is done at the GPU.

@@

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observe dramatic execution time
increase, up to 9.4X, in Raspberry Pi 3 as we increase the number of
co-scheduled tasks. We also observe increased control loop execution
timing in Intel Up and TX2, but the degree of the increase is not as
dramatic as the Pi3. Compared to their respective solo timings (i.e.,
the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increase, respectively. This is somewhat suprising
because Raspberry Pi 3's cores are in-order architecture based while
the cores in Intel Up and NVIDIA TX2 are out-of-order architecture
based and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.
